% =========================================================================
% SciPost LaTeX template
% Version 1e (2017-10-31)
% =========================================================================

% For submitting a paper to SciPost Physics: 
\documentclass[submission, Phys]{SciPost}

\usepackage{multirow}
 \usepackage[utf8]{inputenc} 

\linenumbers

\begin{document}

% title
\begin{center}{\Large \textbf{
  Constraining new physics from Higgs measurements with\\[1mm] Lilith: update to LHC Run~2 results}}\end{center}

% Authors; mark the corresponding author with a superscript *.
\begin{center}
Thi Nhung Dao\textsuperscript{1},
Sabine Kraml\textsuperscript{2*},
Duc Ninh Le\textsuperscript{1},
Loc Tran Quang\textsuperscript{1}
\end{center}

% Affiliations
\begin{center}
{\bf 1} Institute For Interdisciplinary Research in Science and Education, ICISE,\\ 590000, Quy Nhon, Vietnam\\
{\bf 2} Laboratoire de Physique Subatomique et de Cosmologie, Universit\'e Grenoble-Alpes,\\ CNRS/IN2P3, 53 Avenue des Martyrs, F-38026 Grenoble, France\\
% email address of corresponding author
* sabine.kraml@lpsc.in2p3.fr
\end{center}

\begin{center}
\today
\end{center}

% For convenience during refereeing: line numbers
%\linenumbers

\section*{Abstract}
{\bf
Lilith is public python library for constraining new physics from Higgs signal strength measurements. 
We here present version 2.0 of Lilith together with an updated database which includes the full set 
of ATLAS and CMS Run~2 Higgs results for 36~fb$^{-1}$.  
Both the code and the XML database where extended from the ordinary Gaussian approximation employed in 
Lilith-1.1 to using variable Gaussian and Poisson distributions.  Moreover, Lilith can now make use of correlation 
matrices  of arbitrary dimension. 
We provide detailed validations of the implemented experimental results as well as 
a status of global fits for {\it i)} reduced Higgs couplings and {\it ii)} Two-Higgs-doublet models of Type-I and Type-II. 
Lilith-2.0 is available on GitHub and ready to be used to constrain a wide class of new physics scenarios.}


% include a table of contents if paper is longer than 6 pages
%\vspace{10pt}
%\noindent\rule{\textwidth}{1pt}
%\tableofcontents\thispagestyle{fancy}
%\noindent\rule{\textwidth}{1pt}
%\vspace{10pt}


%===================================================================================
\section{Introduction} \label{sec:intro}
%===================================================================================

Introduce Higgs couplings fits and  {\tt Lilith}~\cite{Bernon:2015hsa} .......  \\\
...........\\
...........\\
...........\\
...........\\
...........\\
...........\\


%%% Extended XML format %%%
\input{s2_xmlformat.tex}

%%% Likelihood %%%
\input{s3_likelihood.tex}

%%% ATLAS and CMS results included in the database update %%%
\input{s4_data.tex}


%===================================================================================
\section{Status of Higgs coupling fits}
%===================================================================================


%===================================================================================
\section{Conclusion}
%===================================================================================
 must include a conclusion.

%===================================================================================
\section*{Acknowledgements}
%===================================================================================

S.K.~thanks W.~Adam, R.~Sch\"ofbeck, W.~Waltenberger and N.~Wardle for helpful discussions. 
This work was supported in part by the IN2P3 theory project 
``LHC-itools: methods and tools for the interpretation of the LHC Run~2 results for new physics''. 
D.T.N.\ thanks the LPSC Grenoble for hospitality and financial support for a research visit within the LHC-itools project. 
L.T.Q.\ thanks the ICISE ...


%===================================================================================
\begin{appendix}
%===================================================================================

\section{Overview of XML data files}

\section{Implementation of 2D Poisson likelihood with correlation}


\end{appendix}


%===================================================================================
% References
%===================================================================================

% \bibliographystyle{SciPost_bibstyle} % Include this style file here only if you are not using our template
\bibliography{references.bib}

\nolinenumbers

\end{document}
